\documentclass[preprint,1p]{elsarticle}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{epstopdf}
\usepackage{bmpsize}
\usepackage{epsfig}
\usepackage{hyperref}
\usepackage[english]{varioref}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{dcolumn}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage[mathcal]{eucal}
\usepackage{mathrsfs}
\usepackage{color, colortbl}
\usepackage{microtype}
\usepackage{longtable}
\usepackage[toc,page]{appendix}
\usepackage{bm}
\usepackage{pifont}
\usepackage{fleqn}
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{fullpage}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}

\title{{\bf Null controllability of a nonlocal heat equation with integral kernel}}

\author[rvt,els]{Umberto Biccari \corref{cor1}}
\ead{umberto.biccari@deusto.es - u.biccari@gmail.com}

\author[rvt,els]{V\'ictor Hern\'andez-Santamar\'ia}
\address[rvt]{DeustoTech, University of Deusto, 48007 Bilbao, Basque Country, Spain.}
\address[els]{Facultad de Ingenier\'ia, Universidad de Deusto, Avenida de las Universidades 24, 48007 Bilbao, Basque Country, Spain. \texttt{umberto.biccari@deusto.es, u.biccari@gmail.com, victor.santamaria@deusto.es}}

\cortext[cor1]{Corresponding author.} 

\begin{document}           
	
	\begin{abstract}
		We consider a linear nonlocal heat equation in a bounded domain $\Omega\subset\mathbb{R}^d$ with Dirichlet boundary conditions. The non-locality is given by the presence of an integral kernel. We analyze the problem of controllability when the control acts on a open subset of the domain. It is by now known that the system is null-controllable when the kernel is time-independent and analytic or, in the one-dimensional case, in separated variables. In this paper we relax this assumption and we extend the result to a more general class of kernels. Moreover, we get explicit estimates on the cost of null-controllability.
	\end{abstract}
	
	\begin{keyword}
		Null controllability \sep heat equation \sep nonlocal terms \sep Carleman inequalities
		\\
		\MSC[2010] 93B05, 93B07, 93C20.
	\end{keyword}
	
	\maketitle
	
\end{document}	